---
title: "Project demo"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
library(tidyverse)
library(tidybayes)
library(tidymodels)
library(rstan)
library(rstanarm)
library(bayesplot)
library(bayesrules)
library(broom.mixed)
library(pracma)
library(probably)
library(here)
library(DT)
hotel <- read.csv("https://raw.githubusercontent.com/yiyangshi-hub/STAT454-Project/main/hotel_bookings.csv")
```
## Introduction

>This data set contains booking information for a city hotel and a resort hotel, and includes information such as when the booking was made, length of stay, the number of adults, children, and/or babies, and the number of available parking spaces, among other things.

>The data is originally from the article Hotel Booking Demand Datasets, written by Nuno Antonio, Ana Almeida, and Luis Nunes for Data in Brief, Volume 22, February 2019.

>The data was downloaded and cleaned by Thomas Mock and Antoine Bichat for #TidyTuesday during the week of February 11th, 2020.
source: https://www.kaggle.com/jessemostipak/hotel-booking-demand

```{r }
description <- c("city hotel or resort hotel","if the order is canceled","# of days between order been placed and arrival","Year of arrival date","Month of arrival date","Week number of year for arrival date","Day of arrival date","# of weekend nights","# of week nights","# of adults","# of children","# of babies","# of meal included","country name","Market segment designation:TA means Travel Agents, TO means Tour Operators","Booking distribution channel","if the guest has ordered this hotel before","# of previous cancellation","# order than did not cancel","reserved room type","assigned room type","Number of changes made","if the customer made deposit or not","ID of travel agency","ID of company that made the booking","waiting days before order confirmed","Type of booking","Average Daily Rate as defined by dividing the sum of all lodging transactions by the total number of staying nights","# of parking required","# of special request","Reservation last status","Reservation last status date")
codebook <- data.frame(variable = names(hotel),description = description)
```

```{r}
datatable(codebook)
```

### Data Clean up
```{r}
hotel_clean <- hotel %>% 
  select(-reservation_status, -reservation_status_date,-company, -arrival_date_day_of_month, -days_in_waiting_list, -agent) %>% 
  filter(country %in%
           c("AUT","BEL","BRA","CHE","CHN","CN","DEU","ESP","FRA","GBR","IRL",
             "ISR","ITA","NLD","NOR","POL","PRT","RUS","SWE","USA")) %>% 
  mutate(is_canceled = factor(is_canceled),
         hotel = factor(hotel),
         arrival_date_year = factor(arrival_date_year),
         arrival_date_month = factor(arrival_date_month),
         arrival_date_week_number = factor(arrival_date_week_number),
         meal = factor(meal),
         market_segment = factor(market_segment),
         distribution_channel = factor(distribution_channel),
         is_repeated_guest = factor(is_repeated_guest),
         reserved_room_type = factor(reserved_room_type),
         assigned_room_type = factor(assigned_room_type),
         deposit_type = factor(deposit_type),
         customer_type = factor(customer_type),
         previous_cancellations = factor(previous_cancellations),
         country = factor(country),
         ) %>% 
  na.omit()

set.seed(123)
hotel_sub <- hotel_clean %>% sample_n(1000)
```

```{r}
hotel_sub%>%
  head()
```

### Data Visualization
> In deciding whether the hotel is going to be canceled, we are curious in if the type of the hotel will affect the result. 

> First, we construct a plot for the type of hotel vs is_canceled.

```{r}
hotel_sub %>% 
  ggplot(aes(x = hotel)) +
  geom_bar()

hotel_sub %>% 
  ggplot(aes(x = hotel, fill = is_canceled)) +
  geom_bar(position = "fill")
```

> Then we see that in general, there are more city hotel than resort hotel in our dataset. However, when looking at the hotels that have been canceled, it is more likely for the City Hotel to be canceled than Resort Hotel. 

> Then we may wondering if this can be explained by the customers' own behavior, eg. some customers are more likely to cancel the hotel than others. Then we look at previous cancellations which may reflect the customers behaviors.

```{r}
hotel_sub %>% 
  ggplot(aes(x = previous_cancellations, fill = is_canceled)) +
  geom_bar(position = "fill")
```

> From the graph above, we can see that those who did not cancel last time are also less likely to cancel this time than those who did cancel. 

> We may wondering if we could combine these information together.

```{r}
hotel_sub %>% 
  ggplot(aes(x = hotel, fill = previous_cancellations)) +
  geom_bar(position = "fill")
```

> It is clear that for those who previously canceled, there are more City Hotel than Resort Hotel.

> Thus, we would love to see how this affect the cancellation result.

```{r}
ggplot(hotel_sub, aes(x = hotel, y = is_canceled, color = previous_cancellations)) +
  geom_jitter(height = 0.25)
```

> We can see a clear cluster that those which is a City Hotel and who has previously canceled the hotel would devote the most cases to the hotel cancellations. Hotel type and previous_cancellations are 2 strong predictors.

> So we may wondering what other predictors, like Hotel type and previous_cancellations, can be used to model the hotel cancellations. Then we would dig deeper into model building.

## Model building

### Bayesian Logistic Regression Model
> Since our Y is is_canceled, which is a categorical variable so that we think a logistic regression would characterize this behaviour.

> Our fist model will be using all the 26 variables (expect is_canceled, which is our Y) to build a weakly informative logistic regression model.

To model the binary response variable $Y\in \{0,1\}$ by predictors $X_1,X_2...X_{26}$, suppose we collect n data points. Let $(Y_i, X_i)$ denotes the observed data on each case $i\in \{1, 2, ..., n\}$. Thus the Bayesian Logistic Regression model is as follows:

$$\begin{array}{rll}
Y_i | \beta_0, \beta_1,...,\beta_{26}, \sigma & \stackrel{ind}{\sim} \text{Bern}(\pi_i) & \text{where } \log\left(\frac{\pi_i}{1 - \pi_i}\right) = \beta_0 + \beta_1 X_1 + \beta_2 X_2 +...+\beta_{26} X_{26} \\
&& \text{equivalently, } \frac{\pi_i}{1 - \pi_i} = e^{\beta_0 + \beta_1 X_1 + \beta_2 X_2 +...+\beta_{26} X_{26}} \\ && 
\text{ and } \pi_i = \frac{e^{\beta_0 + \beta_1 X_1 + \beta_2 X_2 +...+\beta_{26} X_{26}}}{e^{\beta_0 + \beta_1 X_1 + \beta_2 X_2 +...+\beta_{26} X_{26}} + 1}\\
\beta_{0c} & \sim N(m_0, s_0^2) & \\
\beta_1    & \sim N(m_1, s_1^2) & \\
\beta_2    & \sim N(m_2, s_2^2) & \\
          &...\\
\beta_{26}    & \sim N(m_{26}, s_{26}^2) & \\
\end{array}$$

**NOTES:**

- The priors on $(\beta_0, \beta_1, ... \beta_{26})$ are independent of one another.

- $\beta_1,\beta_2..,\beta_{26}$ represent the coefficient of predictors $X_{1},X_{2}...X_{26}$ and we also assume that each of the variable follow a normal distribution.

- For interpretability, we state our prior understanding of the model intercept $\beta_0$ through the **centered intercept** $\beta_{0c}$.

- When $X = 0$, $\beta_0$ is the expected *logged* odds for the hotel booking is canceled and $e^{\beta_0}$ is the expected *odds* for the hotel booking is canceled

- For each 1-unit increase in $X_1$, $\beta_1$ is the expected change in the *logged odds of the hotel booking is canceled* and $e^{\beta_1}$ is the expected *multiplicative* change in *odds*. That is
$$\beta_1 = \log(\text{odds}_{x_1+1}) - \log(\text{odds}_{x_1}) \;\; \text{ and } \;\; e^{\beta_1} = \frac{\text{odds}_{x_1+1}}{\text{odds}_{x_1}}$$
- Same formula will apply to the remaining predictors $\beta_2, ..., \beta_{26}$

### Bayesian Lasso Logistic Regression Model

$$\begin{array}{rll}
Y_i | \beta_0, \beta_1,...,\beta_{26}, \sigma & \stackrel{ind}{\sim} \text{Bern}(\pi_i)\\
\beta_{k} & \sim \text{Laplace}(0, 1/\lambda) & \\
\end{array}$$

**NOTES:**

- The priors on $\beta_k$ are independent of one another. We set a laplace prior because the laplace distribution centered at 0, meaning if the coefficient shrink to 0, the corresponding variable will not be considered as one of the predictors in the model. 

- $\beta_k$ represent the coefficient of predictors $X_{1},X_{2}...X_{26}$ and we also assume that each of the variable follow a laplace distribution.

### Horseshoe Prior

$$\begin{array}{rll}
Y_i | \beta_0, \beta_1,...,\beta_{26}, \sigma & \stackrel{ind}{\sim} \text{Bern}(\pi_i)\\
\beta_{k}|\tau,\lambda & \sim \text{N}(0, \tau\lambda_k) & \\
\lambda_k & \sim \text{HalfCauchy}(0,1)\\
\tau & \sim \text{HalfCauchy}(0,\tau_0)
\end{array}$$


**NOTES:**
-  The prior on $\beta_k$ is a model which under the condition of $\lambda_k$ and $\tau$

- The heavy-tailed Cauchy prior on $\lambda_k$ allows individual coefficients to offset and global shrinkage. $\tau$ shares the similar heavy-tailed cauchy prior with $\lambda_k$, but we need to choose $\tau_0$ to determinate how fast the model shrink to 0. 

### Bayesian Logistic Prior
```{r}
log_model <- stan_glm(
  is_canceled ~ ., data = hotel_sub,
  family = binomial,
  chains = 4, iter = 500*2, seed = 123, refresh = 0)

saveRDS(log_model,
        file=here("models","log_model.rds"))
```


### Bayesian Lasso logistic prior
```{r}
#bayesian lasso logistic prior
bayes_lasso_log <- 
  stan_glm(is_canceled ~ .,
         family = binomial(), 
         prior = lasso(df = 10, location = 0, scale = 2.5,autoscale = TRUE),
         prior_intercept = normal(location = 0, scale = 10),
         prior_aux = exponential(rate = 1, autoscale = TRUE),
         data = hotel_sub)

tidy(bayes_lasso_log)
```

```{r}
mcmc_intervals(bayes_lasso_log,
               pars = vars(starts_with("country")))

mcmc_intervals(bayes_lasso_log,
               pars = vars(starts_with("arrival_date_year")))

mcmc_intervals(bayes_lasso_log,
               pars = vars(starts_with("arrival_date_month")))

mcmc_intervals(bayes_lasso_log,
               pars = vars(starts_with("arrival_date_week")))

mcmc_intervals(bayes_lasso_log,
               pars = vars(starts_with("is_repeated_guest"),
                           starts_with("previous_cancellations"),
                           starts_with("distribution_channel"),
                           starts_with("market_segment"),
                           starts_with("meal")))

mcmc_intervals(bayes_lasso_log,
               pars = vars(starts_with("reserved_room_type"),
                           starts_with("assigned_room_type"),
                           starts_with("deposit_type"),
                           starts_with("customer_type")))

mcmc_intervals(bayes_lasso_log,
               pars = vars(lead_time,
                           stays_in_weekend_nights,
                           stays_in_week_nights,
                           adults,
                           children,
                           babies,
                           previous_bookings_not_canceled,
                           booking_changes,
                           adr,
                           required_car_parking_spaces,
                           total_of_special_requests))
```

```{r,eval=FALSE}
hotel_lasso <- hotel_clean %>% 
  select(-meal, -lead_time, -stays_in_weekend_nights, -stays_in_week_nights, -adults, -previous_bookings_not_canceled, -booking_changes, -adr)


set.seed(123)
hotel_lasso <- hotel_lasso %>% sample_n(1000)


bayes_lasso_log_updated <- 
  stan_glm(is_canceled ~ .,
         family = binomial(), 
         prior = lasso(df = 10, location = 0, scale = 2.5,autoscale = TRUE),
         prior_intercept = normal(location = 0, scale = 10),
         prior_aux = exponential(rate = 1, autoscale = TRUE),
         prior_PD = FALSE,
         data = hotel_lasso)

saveRDS(bayes_lasso_log_updated,
        file=here("models","bayes_lasso_log_updated.rds"))
```

```{r}
tidy(bayes_lasso_log_updated, 
     effects = c("fixed", "aux"),
     conf.int = TRUE, 
     conf.level = 0.8)

set.seed(112)
prediction_summary_cv(model = bayes_lasso_log_updated, 
                      data = hotel_lasso, 
                      k = 10)
```


```{r}
# MCMC diagnostic
mcmc_trace(bayes_lasso_log_updated,
           pars = vars(starts_with("country")))

mcmc_trace(bayes_lasso_log_updated,
           pars = vars(starts_with("arrival_date_year")))

mcmc_trace(bayes_lasso_log_updated,
           pars = vars(starts_with("arrival_date_month")))

mcmc_trace(bayes_lasso_log_updated,
           pars = vars(starts_with("arrival_date_week")))

mcmc_trace(bayes_lasso_log_updated,
           pars = vars(starts_with("is_repeated_guest"),
                           starts_with("previous_cancellations"),
                           starts_with("distribution_channel"),
                           starts_with("market_segment"),
                           starts_with("meal")))

mcmc_trace(bayes_lasso_log_updated,
               pars = vars(starts_with("reserved_room_type"),
                           starts_with("assigned_room_type"),
                           starts_with("deposit_type"),
                           starts_with("customer_type")))

mcmc_trace(bayes_lasso_log_updated,
               pars = vars(children,
                           babies,
                           required_car_parking_spaces,
                           total_of_special_requests))
```


### Horseshoe prior
```{r, eval=FALSE}

# horseshoe prior
p0 <- 10
tau0 <- p0/(26-p0) * 1/sqrt(1000)
hs_prior <- hs(df=1, global_df=1, global_scale=tau0)

log_hs_model <- stan_glm(is_canceled~.,
                  data = hotel_sub,
                  family = binomial(link = "logit"), 
                  prior = hs_prior, 
                  chains = 4, 
                  iter = 500*2, 
                  seed = 123,
                  control = list(adapt_delta = 0.999,
                                 stepsize = 0.001,
                                 max_treedepth = 25),
                  refresh = 0)
```

```{r}
log_hs_model <- readRDS(here("models","log_hs_model.rds"))
```

```{r}
pp_check(log_hs_model)
```


```{r}
mcmc_intervals(log_hs_model,
               pars = vars(starts_with("country")))

mcmc_intervals(log_hs_model,
               pars = vars(starts_with("arrival_date_year")))

mcmc_intervals(log_hs_model,
               pars = vars(starts_with("arrival_date_month")))

mcmc_intervals(log_hs_model,
               pars = vars(starts_with("arrival_date_week")))

mcmc_intervals(log_hs_model,
               pars = vars(starts_with("is_repeated_guest"),
                           starts_with("previous_cancellations"),
                           starts_with("distribution_channel"),
                           starts_with("market_segment"),
                           starts_with("meal")))

mcmc_intervals(log_hs_model,
               pars = vars(starts_with("reserved_room_type"),
                           starts_with("assigned_room_type"),
                           starts_with("deposit_type"),
                           starts_with("customer_type")))

mcmc_intervals(log_hs_model,
               pars = vars(lead_time,
                           stays_in_weekend_nights,
                           stays_in_week_nights,
                           adults,
                           children,
                           babies,
                           previous_bookings_not_canceled,
                           booking_changes,
                           adr,
                           required_car_parking_spaces,
                           total_of_special_requests))
```

> With the mcmc_interval above, we can eliminate the variables whose interval shrinks to zero, meaning they don't have plenty of contribution on predicting the hotel cancellation. We will eliminate the variables: lead_time, adults, babies, stays_in_weekend_nights, stays_in_week_nights, previous_bookings_not_canceled, booking_changes, adr, reserved_room_type, meal

```{r}
hotel_hs <- hotel_clean %>% 
  select(-lead_time, -adults, -babies, -stays_in_weekend_nights, -stays_in_week_nights, -previous_bookings_not_canceled, -booking_changes, -adr, -reserved_room_type, meal)

set.seed(123)
hotel_hs <- hotel_hs %>% sample_n(1000)


log_hs_model_updated <- stan_glm(is_canceled~.,
                  data = hotel_hs,
                  family = binomial(link = "logit"), 
                  prior = hs_prior,
                  prior_PD = FALSE,
                  chains = 4, 
                  iter = 500*2, 
                  seed = 123,
                  control = list(adapt_delta = 0.999,
                                 stepsize = 0.001,
                                 max_treedepth = 25),
                  refresh = 0)

saveRDS(log_hs_model_updated,
        file=here("models","log_hs_model_updated.rds"))
```


```{r}
log_hs_model_updated <- readRDS(here("models","log_hs_model_updated.rds"))
```

```{r}
# MCMC diagnostic
mcmc_trace(log_hs_model_updated,
           pars = vars(starts_with("country")))

mcmc_trace(log_hs_model_updated,
           pars = vars(starts_with("arrival_date_year")))

mcmc_trace(log_hs_model_updated,
           pars = vars(starts_with("arrival_date_month")))

mcmc_trace(log_hs_model_updated,
           pars = vars(starts_with("arrival_date_week")))

mcmc_trace(log_hs_model_updated,
           pars = vars(starts_with("is_repeated_guest"),
                           starts_with("previous_cancellations"),
                           starts_with("distribution_channel"),
                           starts_with("market_segment"),
                           starts_with("meal")))

mcmc_trace(log_hs_model_updated,
               pars = vars(starts_with("reserved_room_type"),
                           starts_with("assigned_room_type"),
                           starts_with("deposit_type"),
                           starts_with("customer_type")))

mcmc_trace(log_hs_model_updated,
               pars = vars(children,
                           required_car_parking_spaces,
                           total_of_special_requests))
```

```{r}
pp_check(log_hs_model_updated)
pp_check(log_hs_model)
```

```{r}
set.seed(454)
classification_summary_cv(
 model = log_hs_model_updated, data = hotel_hs,
 cutoff = 0.5,
 k = 10)
```

